# Function Usecase


# Generalise your code


The following dataset contains the average summer temperatures per year in Germany. You can download it [here](https://opendata.dwd.de/climate_environment/CDC/regional_averages_DE/seasonal/air_temperature_mean/regional_averages_tm_summer.txt).

The code block below calculates the long term average summer temperature between 1960 and 1989 for Bayern. In the following task we want to generalise this code in a way that we can choose for which years and which state we calculate the average temperature.


```{r}
dwd = read.csv("https://opendata.dwd.de/climate_environment/CDC/regional_averages_DE/seasonal/air_temperature_mean/regional_averages_tm_summer.txt", sep = ";", skip = 1)
knitr::kable(head(dwd))
```


```{r}
# mean temperature in Bayern between 1960 and 1989
mean(dwd[dwd$Jahr >= 1960 & dwd$Jahr <= 1989, "Bayern"])
```




:::{.callout-important}
## Task
* Write a function that calculates the long-term average temperature for a particular region in Germany.
* The function should have three arguments: the region, the start year and the end year.
* The function should return the temperature average between these two year for the specified region.

:::










