# lapply-loops

R has some more specific loop types that work very well with `vectors` and `lists`. They are called `lapply` loops in R and make use of `functions` that are applied over the element of a `vector` or `list`.

The syntax of the `lapply` loop can be a bit confusing at first as it is the other way around as the `for` loop.
The biggest difference is, that `lapply` returns a list of values for every iteration step. So the output of the loop can be assigned directly to a variable.

```{r}
#| echo: true
#| eval: false

result <- lapply(i, FUN)

# compared to:
result <- c()
for(i in x){
  result[i] <- FUN
}
```



There are multiple forms of apply loops. `lapply` and `sapply` only differ in their output format. `apply` is used for `data.frames`.


```{r}
#| eval: false
#| echo: true
lapply() # list apply

sapply() # apply with vector output

apply() # loop over rows or columns of a data.frame
```



```{r}
#| echo: true
lapply(seq(10), function(x){
  x^2
})
```


```{r}
#| echo: true
sapply(seq(10), function(x){
  x^2
})
```












